---
title: "isur_notes"
author: "Donald Sawyer"
date: "August 11, 2016"
output: html_document
---

# Data Notes

Dataset|Description|Location
:-------|:-----------|:-------
`precip`|(v) Contains average rainfall for 70 cities.|R Base packages
`rivers`|(v) Contains the length of various in the US.|`datasets`
`discoveries`|(v) Time series of number of inventions "great" inventions from 1860-1959|R Base packages

# Chapter 3 - Data Descriptions

## Quantitative Data

###Discrete vs. Continuous Data

Take a look at the precip dataset a bit.
`precip` is continuous quantitative data.  The data are in floating point continuous measurements.

```{r}
str(precip)
precip[1:4]
```

What about the `rivers` data?  The measurements here are rounded to the nearest mile, and are thus discrete and not continuous.
It may be useful to make them continuous, but for now, they represent discrte data.
```{r} 
str(rivers)
```

The `discoveries` dataset contains time series data of the number of "great" inventions from 1860-1959 from the 1979 world almanac.
Each entry is an integer (count), and represents *discrete quantitative* data.

```{r}
str(discoveries)
```

### Displaying Quantitative Data
Once you have some quantitative data, it is best to display the data in some way that helps you understand it a little better.

#### Strip charts (dot plots)
**x-axis**: Numerical Scale
**y-axis**
